Wrangling - combine reviews

### 2022-03-08 02-wrangling_reviews.Rmd
save out all reviews too

```{r}
# join up
all_reviews <- chrome_reviews %>% 
  filter(type == "review") %>% 
  select(tool_id = extension_url, user_name, date = date_modified, rating, review_text = text, store) %>% 
  bind_rows(play_reviews %>% rename(review_text = text, tool_id = app_id)) %>% 
  bind_rows(apple_reviews %>% select(tool_id = app_id, user_name, date, rating, review_text, store))

@@

# Simplify tool id for the chrome web store and save our
```{r}
# join it up with the reviews and save out
all_reviews_distinct %>%
  # simplify toolid for chrome web extensions
  mutate(tool_id = if_else(store == "chrome", 
                           str_remove(tool_id, "\\?hl=.+") %>%  str_extract("/[^/]+$") %>% str_remove("/"),
                           tool_id)) %>% 
  relocate(tool_id, store) %>% 
  write_csv(here::here("data", "processed", "distinct_reviews.csv"))

>>>>

```{r}
# join up
all_reviews <- chrome_reviews %>% 
  filter(type == "review") %>% 
  # use the unique ending of the URL as tool id
  mutate(tool_id = str_remove(extension_url, "\\?hl=.+") %>%  str_extract("/[^/]+$") %>% str_remove("/")) %>% 
  select(tool_id, user_name, date = date_modified, rating, review_text = text, store) %>% 
  bind_rows(play_reviews %>% rename(review_text = text, tool_id = app_id)) %>% 
  bind_rows(apple_reviews %>% select(tool_id = app_id, user_name, date, rating, review_text, store))

all_reviews %>% 
  write_csv(here::here("data", "processed", "all_reviews.csv"))

@@

# Simplify tool id for the chrome web store and save our
```{r}
# join it up with the reviews and save out
all_reviews_distinct %>%
  # simplify toolid for chrome web extensions
  relocate(tool_id, store) %>% 
  write_csv(here::here("data", "processed", "distinct_reviews.csv"))
